Bayesian Inference from Time Series: Information Loss and the Whittle Likelihood

### 2018-03-06 doc/ms.tex
Abstract and intro writing

\abstract{\noindent I investigate the information content of a time series
          dataset for inferring a parameter of interest. }

@@

@@

@@

>>>>

\abstract{\noindent Inference from a time series dataset can be performed
          either with the raw time series data, or after transformation to
          the fourier domain. In the latter case, Whittle's approximation to
          the likelihood function is computationally convenient. However, the
          question of how much information is lost remains open --- in many
          cases, the cost of extra computing time might be worth the benefits
          of preserving all of the information from the raw time series data.
          In this paper I investigate this question using numerical experiments
          to quantify the mutual information between a dataset and a parameter
          under the exact and the Whittle likelihoods.}

@@

Just as probability theory (used in the `Bayesian' way)
quantifies the degree to which one statement or
proposition implies another \citep{knuth_skilling},
information theory describes the
degree to which resolving one question would resolve another
\citep{knuth_questions, vanerp}.

@@

\bibitem[Knuth(2005)]{knuth_questions}
Knuth, K.H. Toward question-asking machines: The logic of questions and the inquiry calculus. In
Proceedings of the 10th International Workshop On Artificial Intelligence and Statistics, Barbados, 6–8
January 2005.

\bibitem[Knuth and Skilling(2012)]{knuth_skilling}
Knuth, Kevin H., and John Skilling. ``Foundations of inference.''
Axioms 1, no. 1 (2012): 38-73.

@@

\bibitem[van Erp et al.(2017)]{vanerp}
van Erp, H. R., Ronald O. Linger, and Pieter HAJM van Gelder. ``Inquiry Calculus and the Issue of Negative Higher Order Informations.'' Entropy 19, no. 11 (2017): 622.
